Explaining the reportedly over-massive black holes in early-type galaxies with intermediate-scale discs

### 2015-10-28 papers/ellicular/ellicular.tex
hes crazy

%\title[Non over-massive black holes in early-type galaxies]{Early-type galaxies with intermediate-scale discs and their (non over-massive) black holes}
\title[Non over-massive black holes in early-type galaxies]{Non over-massive black holes in early-type galaxies with intermediate-scale discs}

@@

\begin{abstract}
{\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
%with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we show that decompositions in which the disc remains embedded within the spheroid, 
labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of early-type galaxies 
%intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
with intermediate-scale discs. 
Intermediate-scale discs have often been confused with large-scale discs, and modelled accordingly; 
when this happens, the spheroid luminosity is considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of galaxies with intermediate-scale discs (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when these galaxies are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes. }

@@

{\bf The awareness that many early-type galaxies contain stellar discs dates back several years 
\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,bender1988,bender1990,capaccioli1988,franx1989,
nieto1988,nieto1991,rixwhite1990,rixwhite1992,vandenbergh1990,scorzabender1990,scorzabender1995,
simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999}. 
Since then, it has been well known that 
the identification of a stellar disc in an early-type galaxy based on the galaxy's photometric properties 
is subjected to inclination effects. 
This problem has been overcome with kinematic analysis (e.g.~the ATLAS$^{\rm 3D}$ survey, \citealt{cappellari2011}), 
which allows one to determine the presence of a rotationally-supported component in a galaxy 
in a way that can be nearly insensitive to projection effects \citep{cappellari2007,emsellem2007}. 

@@

Most early-type galaxies are classified as ``fast rotators'' \citep{atlas3dIII,scott2014}, 

@@

of 

@@

i.e.~a disc-dominated central fast rotator that continues to be fast rotating beyond one half-light radius, 
(ii) a discy elliptical galaxy \citep{kormendybender1996} 

@@

i.e.~a spheroid-dominated central fast rotator that becomes slow rotating beyond $1-2$ half-light radii, and  

@@

This is sequence is analogue to that illustrated in Figure 2 of \cite{cappellari2011}, 

@@

and the ``shape'' of the ellipticity (assuming that the disc inclination is not close to face-on) and specific angular momentum profiles. 
In general, stellar discs are intrinsically flat and circular; 
their ellipticity, dictated by their inclination to our line of sight, is fixed. 

@@

This approach can be taken to the next level by inspecting the isophotes for discy structures and checking the velocity line profiles for asymmetry 
(e.g.~\citealt{scorzabender1995} and references therein; \citealt{scorza1998}). \\
While some recent studies -- well aware of this problematic -- have correctly distinguished between large- and intermediate-scale discs, 

@@

who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 

@@

Indeed, \citeauthor{graham2011} (\citeyear{graham2011}, his Figure 7) warned about such erroneous fits to spiral galaxies. 
This bias has led to the rejection of many early-type galaxy decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 

@@

As mentioned before, a photometric analysis allows one to identify the presence and the radial extent of a disc in an early-type galaxy 

@@

Therefore, the best results are obtained when photometry and kinematics are combined together. 

@@

which is used to constrain galaxy evolution models. \\
This paper is structured as follows. 

@@

Finally, in Section \ref{sec:disc} we discuss our results in terms of galaxy evolution. }

%There are currently two well-known types of stellar discs in galaxies.
%The first are the large-scale discs (with exponential scale lengths of a few kiloparsec)
%that dominate the light at large radii in spiral and lenticular galaxies;
%the second are the small (tens to a couple of hundred parsec) nuclear discs observed in both early- and late-type galaxies
%(e.g.~\citealt{scorzavandenbosch1998,rest2001,balcells2007,ledo2010}).
%The origin of the nuclear discs has been speculated to arise from the infall of small satellite galaxies or gas clouds.
%The origin, or at least the on-going feeding and growth, of the large-scale discs has been attributed to cold gas flows,
%gas rich mergers and halo accretion events
%(e.g.~\citealt{whiterees1978,whitefrenk1991,navarrobenz1991,barneshernquist1992,khochfarsilk2006,dekel2009nat,ceverino2010,
%ceverino2012,conselice2012,rubin2012,martini2013,ueda2014}),
%and a thorough review can be found in \citet{combes2014arX,combes2014pro}.
%On the other hand, intermediate-sized discs have not received the same level of attention
%as their nuclear and large-scale homologues and
%they have at times been labelled and rejected as ``unphysical'' when detected.
%Here we focus on the increasingly overlooked occurence of intermediate-scale discs in galaxies with directly measured black hole masses.
%We report on the photometric and kinematical signatures of these intermediate-sized stellar discs,
%and the impact they have on the (black hole mass)-to-(spheroid stellar mass) ratio
%which is used to constrain galaxy evolution models. \\
%The majority of stellar discs have some level of inclination with respect to our line-of-sight,
%and this makes them appear elliptical (rather than round) when seen in projection on the sky.
%This can help one distinguish them from the more spherically-shaped spheroids.
%Identifying the radial extent of these discs with respect to the spheroid can however be subtle.
%Two-dimensional kinematic maps represent an important diagnostic tool for this purpose.
%Most early-type galaxies are classified as ``central fast rotators'' \citep{franx1989,atlas3dIII,scott2014},
%that is, they are rapidly rotating within their half-light radius.  
%However, more extended kinematic maps \citep{arnold2014} reveal that 
%some of the central fast rotators continue to be fast rotating at large radii, 
%whereas other central fast rotators become slow rotators in their outer regions.
%A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
%is a signature of a large-scale disc, 
%while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
%indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 
%Unfortunately, such extended kinematic maps are not yet available for large numbers of galaxies in the local Universe. 
%Nevertheless, the ellipticity profile of a galaxy's isophotes can help identify the extent of stellar discs in early-type galaxies. \\
%Building on the investigation of \cite{rixwhite1990}, 
%the toy model shown in Figure \ref{fig:model} illustrates the typical ellipticity profile 
%($\epsilon = 1 - b/a$, where $b/a$ is the ratio of minor-to-major axis length) of 
%(i) a disc-dominated early-type galaxy, 
%comprised of a large-scale disc which dominates the light at large radii over a relatively smaller encased bulge, 
%(ii) a spehroid-dominated early-type galaxy with an additional nuclear stellar disc, 
%and (iii) an early-type galaxy composed of an intermediate-scale disc embedded in a relatively larger spheroid 
%which dominates the light at large radii. 
%In general, stellar discs are intrinsically flat and circular; 
%their ellipticity, dictated by their inclination to our line of sight, is fixed. 
%Spheroids are often rounder than the observed projection on the sky of their associated discs, 
%thus their average ellipticity is often lower than that of their disc. 
%An ellipticity profile that increases with radius can be ascribed to an inclined disc that becomes progressively more important at large radii, 
%whereas a radial decrease of ellipticity signifies the opposite case. 
%This approach can be taken to the next level by inspecting the isophotes for discy structures and checking the velocity line profiles for asymmetry 
%(e.g.~\citealt{scorzabender1995} and references therein; \citealt{scorza1998}). \\
%The awareness that many so-called ``elliptical'' galaxies actually contain stellar discs 
%dates back many years 
%\citep{michard1984,djorgovski1985,carter1987,capaccioli1987,capaccioli1988,franx1989,nieto1988,nieto1991,rixwhite1990,rixwhite1992,
%vandenbergh1990,bender1990,scorzabender1990,scorzabender1995,
%simienmichard1990,cinzanovandermarel1993,donofrio1995,graham1998fornax,scorza1998,scorzavandenbosch1998,bendersaglia1999} and, 
%more recently, intermediate-scale discs were anything but unfamiliar to \cite{kormendybender2012} and \cite{krajnovic2013etal}. 
%However, intermediate-scale discs have been missed by many galaxy modellers of late, 
%who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions in which the disc does not dominate over the spheroid at large radii 
%as is observed with spiral galaxies. 
%Indeed, \citeauthor{graham2011} (\citeyear{graham2011}, his Figure 7) warned about such erroneous fits to spiral galaxies. 
%This bias has led to the rejection of many early-type galaxy decompositions similar to that illustrated in the middle panel of Figure \ref{fig:model}. 
%Unsurprisingly, studies affected by this bias have not obtained spheroid/disc decompositions with a spheroid-to-total ratio larger than $0.6 - 0.8$ 
%(e.g.~\citealt{gadotti2008,head2014,querejeta2015,mendezabreu2015}).
%In this paper we investigate the influence this has had on research pertaining to supermassive black hole mass scaling relations involving the host spheroid. \\
%This paper is structured as follows.
%In Section \ref{sec:gal} we present a detailed photometric analysis of three galaxies with intermediate-scale discs (Mrk 1216, NGC 1332, and NGC 3115)
%and we briefly describe another five galaxies with intermediate-scale discs (NGC 821, NGC 1271, NGC 1277, NGC 3377, and NGC 4697)
%already modelled by us elsewhere in the literature.
%We compare our photometric analysis with the kinematical information available from the literature,
%and explain the differences between our galaxy models and past decompositions.
%In Section \ref{sec:mm} we explore the important implications this has for the (black hole mass)-(spheroid stellar mass) diagram.
%Finally, in Section \ref{sec:disc} we discuss our results in terms of galaxy evolution.
%%and we present the location of ellicular galaxies, relative to other galaxies, in the Hubble grid.

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{discmodel.eps}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a disc-dominated central fast rotator (lenticular galaxy), composed of a bulge encased in a large-scale disc. 
The right panel displays a spheroid-dominated slow rotator (elliptical) with (an optional) nuclear stellar disc. 
The middle panel presents a spheroid-dominated central fast rotator (discy elliptical) with an intermediate-sized disc embedded in the spheroid. }
\label{fig:model}
\end{center}
\end{figure}

@@

\subsection{NGC 3115}
The presence of a disc in the {\bf central fast rotator} NGC 3115 is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
Such rings are common in early-type galaxies \citep{michardmarchal1993}.
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

@@

\subsubsection{NGC 3377}
\cite{lasker2014data} modelled the {\bf central fast rotator} NGC 3377 with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total flux ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total flux ratio of $0.94$.

@@

\subsubsection{NGC 4697}
The {\bf central fast rotator} NGC 4697 represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total flux ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.89$. \\

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{n1332_image}
\includegraphics[width=0.49\columnwidth]{n1332_unsharp} \\
\includegraphics[width=1.03\columnwidth]{n1332_decomposition.pdf}
\caption{NGC 1332.
Same as Figure \ref{fig:n3115}, except for the following. 
The surface brightness profile extends out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
The empty points are data excluded from the fit. 
}
\label{fig:n1332}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{mrk1216_image.jpeg}
\includegraphics[width=0.49\columnwidth]{mrk1216_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{mrk1216_decomposition.pdf}
\caption{Mrk 1216. 
Same as Figure \ref{fig:n3115}, except for the following. 
The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right).
The surface brightness profile extends out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components:
{\bf red solid = S\'ersic (spheroid), blue dashed = exponential (disc). }
}
\label{fig:m1216}
\end{center}
\end{figure}

@@

Acknowledging the correct structure of galaxies with intermediate-scale discs is important to properly understand their origin. 
According to the current paradigm of cosmological structure evolution, 
the genesis of massive early-type galaxies is characterized by two distinct phases: ``in-situ'' and ``ex-situ''. 
The first phase takes place in a young Universe (within its first $4~\rm Gyr$), 
when cold gas inflows produced short and intense bursts of star formation 
that created compact and dense conglomerates of stars with high velocity dispersion (e.g.~\citealt{prieto2013}). 
These naked and compact conglomerates, named ``red nuggets'' \citep{damjanov2009}, 
have been observed at high-redshift with half-light sizes of 1--2 kpc \citep{daddi2005,trujillo2006,vandokkum2008}.
In the second phase (last $10~\rm Gyr$), discs and stellar envelopes 
were accreted around these primordial conglomerates and the external parts of today's galaxies assembled on scales of 2--20 kpc 
(e.g.~\citealt{driver2013}). \\
Today's Universe is populated by an abundance of compact, massive spheroids, 
with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{graham2013review,GDS2015}. 
Some of these local compact massive spheroids are encased within a large-scale disc, 
that is to say they are the bulges of some lenticular and spiral galaxies.  
Over the last $10~\rm Gyr$ their spheroids have evolved by growing a relatively flat disc (e.g.~\citealt{pichon2011,danovich2012,stewart2013})
-- rather than a three-dimensional envelope -- 
which has increased the galaxy size but preserved the bulge compactness. 
The other compact massive spheroids of today's Universe belong to some galaxies with intermediate-scale discs. 
Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact intermediate-scale disc galaxies 
with purely old ($>10~\rm Gyr$) stellar populations. 
These galaxies have undergone the lowest degree of disc growth. \\
In addition to the observational clues as to the actual physical components in galaxies with intermediate-scale discs, 
one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
plus large-scale disc plus outer envelope. 
If they were such three-component systems, then one would have two possibilities. 
The first possibility is that these galaxies were already fully assembled $10~\rm Gyr$ ago; 
this would explain their old stellar populations, 
but it would also imply that their discs and envelopes had already formed during the first $4~\rm Gyr$ of the Universe, 
in disagreement with the current cosmological picture. 
The second possibility is that only their inner bulges (with sizes of 0.1--0.2 kpc, 
according to past decompositions) originated in the first $4~\rm Gyr$ 
and they subsequently accreted a substantial disc and envelope. 
If this was correct, then we would observe high-redshift, star-like, naked bulges with stellar masses 
within a factor of a few times the currently observed red nuggets but sizes which are $10$ times smaller. 
However, a dramatically different expectation is reached 
if one considers these galaxies today as spheroid-dominated systems with an intermediate-scale disc; 
in this case, both the galaxy size and the spheroid size are compact (1--2 kpc). 
This implies that, among the local descendants of the high-redshift red nuggets, 
the compact intermediate-scale disc galaxies have undergone the lowest degree of disc growth. 
That is, the bulk of a compact intermediate-scale disc galaxy quickly assembled ``in-situ'' in a very young Universe 
and experienced very little evolution over the last $10~\rm Gyr$.

>>>>

%\title[Non over-massive black holes in early-type galaxies]{Early-type galaxies with intermediate-scale discs and their (non over-massive) black holes}
\title[Explaining the reportedly over-massive black holes]
{Explaining the reportedly over-massive black holes in early-type galaxies with intermediate-scale discs}

@@

\begin{abstract}
{\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
%with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we show that decompositions in which the disc remains embedded within the spheroid, 
labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of early-type galaxies 
%intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
with intermediate-scale discs. 
Intermediate-scale discs have often been confused with large-scale discs and incorrectly modelled as such; 
when this happens, the spheroid luminosity is considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of galaxies with intermediate-scale discs (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when these galaxies are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes. }

@@

{\bf The awareness that \emph{many} early-type galaxies contain previously over-looked stellar discs dates back half a century 
\citep{liller1966,michard1984,djorgovski1985,jedrzejewski1987,BenderMoellenhoff1987,
carter1987,capaccioli1987,capaccioli1988,stromstrom1978,bender1988,bender1990,
nieto1988,rixwhite1990,vandenbergh1990,scorzabender1990,scorzabender1995,
simienmichard1990}. 
Not surprisingly, it is well known that 
the identification of a stellar disc in an early-type galaxy, particularly when based on the galaxy's photometric properties, 
is subject to inclination effects. 
As predicted by \cite{carter1987}, this problem is largely overcome with kinematic analyses 
(e.g.~\citealt{franx1989,nieto1991,rixwhite1992,cinzanovandermarel1993,donofrio1995,graham1998fornax}, 
and the ATLAS$^{\rm 3D}$ survey, \citealt{cappellari2011}), 
which allow one to determine the presence of a rotationally-supported component 
in a way nearly insensitive to projection effects \citep{mcelroy1983,cappellari2007,emsellem2007}. 

@@

Studying both the surface brightness profiles and the ellipticity profiles 
(a concept pioneered by \citealt{liller1960})\footnote{\cite{liller1960} 
used ellipticity profiles to help identify elliptical and spiral galaxy type.} 
of early-type galaxies in the Virgo cluster -- including those with elliptical (E), spindle and lenticular (S0) isophotes -- 
\cite{liller1966} drew attention to the observation that many of the galaxies displayed 
``characteristics intermediate between those of type E and type S0'', 
and she classified them as ``ES'' galaxies\footnote{\cite{strom1977} and \cite{stromstrom1978} 
classified the intermediate ``ES'' galaxy type as ``E/S0'', see also \cite{thompson1976}.}.  
Building on this and other investigations of ellipticity profiles (e.g.~\citealt{stromstrom1978,ditullio1979}), 
\cite{michard1984} used the classification ``S0-like'' for these early-type galaxies with humped ellipticity profiles, 
dominated by a somewhat edge-on disc at intermediate radii.  
\cite{nieto1988} identified two dozen such spheroid-dominated early-type galaxies, 
whose discs do not prevail at large radii, 
and referred to them as ``disk-ellipticals'' (or ``disky ellipticals'', \citealt{simienmichard1990}) 
thereby more closely associating them with elliptical galaxies than lenticular galaxies.   
However, as noted by \cite{nieto1988}, unless the orientation of the disc is favourable 
(i.e.~somewhat edge-on), it can be missed.  
The same is true when searching for pointy isophotes that are shaped by the combination of the spheroid and a near edge-on disc 
(e.g.~\citealt{carter1978,carter1987,jedrzejewski1987,BenderMoellenhoff1987}). 
Today, most early-type galaxies are classified as ``fast rotators\footnote{The term 
``fast rotator'' is of course not new for describing certain early-type galaxies (e.g.~\citealt{bertinstiavelli1984,lakedressler1986}).}'' 
\citep{atlas3dIII,scott2014}, 

@@

of: 

@@

i.e.~a disc-dominated central fast rotator that continues to be fast rotating beyond one half-light radius; 
(ii) a ``discy elliptical'' galaxy \citep{michard1984,nieto1988} 

@@

i.e.~a spheroid-dominated central fast rotator that becomes slow rotating beyond $1-2$ half-light radii; and  

@@

This sequence is analogue to that illustrated in Figure 2 of \cite{cappellari2011}, 

@@

and the ``shape'' of the ellipticity profile (assuming that the disc inclination is not close to face-on) 
and also the specific angular momentum profiles. \\
In general, stellar discs are intrinsically flat and close to circular; 
their apparent ellipticity, dictated by their inclination to our line of sight, is fixed. 

@@

This approach can be taken to the next level by inspecting the isophotes for discy structures 
(e.g.~\citealt{carter1978,carter1987,capaccioli1987,jedrzejewski1987,BenderMoellenhoff1987}) 
and checking the velocity line profiles for asymmetry 
(e.g.~\citealt{franxillingworth1988ic1459,bender1990,rixwhite1992,scorzabender1995}, and references therein; \citealt{scorza1998}). \\
While some recent studies have correctly distinguished between large- and intermediate-scale discs, 

@@

who have labelled as ``unphysical'' \citep{allen2006} those spheroid/disc decompositions 
in which the disc does not dominate over the spheroid at large radii 

@@

Indeed, \citeauthor{graham2001} (\citeyear{graham2001}, his Figure 7) warned about such erroneous fits to late-type galaxies. 
However, this has led to the rejection of many early-type galaxy decompositions 
similar to that illustrated in the top middle panel of Figure \ref{fig:model}. 

@@

As mentioned before, an isophotal analysis allows one to identify the presence and the radial extent of a disc in an early-type galaxy 

@@

Therefore, the best results are obtained when photometry and kinematics are combined together. \\

@@

which is used to constrain galaxy evolution models. 

@@

Finally, in Section \ref{sec:disc} we briefly discuss our results in terms of galaxy evolution 
and we present the location of the ES galaxies relative to other disc galaxies 
in a common classification scheme of Hubble type versus spheroid-to-disc ratio. }

\begin{figure}
\begin{center}
\includegraphics[width=\columnwidth]{discmodel.eps}
\caption{Illustration of the spheroid/disc decomposition of the one-dimensional surface brightness profile, $\mu$, 
the ellipticity profile, $\epsilon$, and the specific angular momentum profile, $\lambda$,
for the three prototype early-type galaxy sub-classes. 
In the flux decompositions, the spheroid (or bulge) and the disc are shown with the red and blue color, respectively. 
The left panel shows a disc-dominated central fast rotator (lenticular galaxy), composed of a bulge encased in a large-scale disc. 
The right panel displays a spheroid-dominated slow rotator (elliptical) with (an optional) nuclear stellar disc. 
The middle panel presents a spheroid-dominated central fast rotator with an intermediate-sized disc embedded in the spheroid. }
\label{fig:model}
\end{center}
\end{figure}

@@

\subsection{NGC 3115}
The presence of a disc in the {\bf central fast rotator} NGC 3115 
{\bf (e.g.~\citealt{strom1977,nieto1988,scorzabender1995}) }
is obvious due to its edge-on orientation (Figure \ref{fig:n3115}). 
Less obvious is the radial extent of this disc, if one only relies on a visual inspection of the galaxy image. 
The ellipticity profile (Figure \ref{fig:n3115}) is consistent with the presence of an intermediate-scale disc. 
Moreover, the kinematics of NGC 3115 \citep{arnold2011n3115} also disprove the presence of a large-scale disc, 
because the galaxy is rapidly rotating only within two galaxy half-light radii ($\sim 2 \times 50~\rm arcsec$), 
and the rotation significantly drops at larger radii.  
The unsharp mask of NGC 3115 (Figure \ref{fig:n3115}) betrays the presence of a faint edge-on nuclear ring, 
which can also be spotted as a small peak in the ellipticity profile 
(at semi-major axis length $R_{\rm maj} \sim 15~\rm arcsec$). 
Such rings are common in early-type galaxies \citep{michardmarchal1993}.
The spheroidal component of NGC 3115 is well described with a \cite{sersic1963} profile.
The highly inclined intermediate-scale disc is better fit with an $n<1$ S\'ersic profile 
(the S\'ersic index $n$ regulates the curvature of the S\'ersic profile) 
rather than with an exponential function, 
as explained by \cite{pastrav2013a}. 
The nuclear ring is modelled with a Gaussian function. \\
In comparison, \cite{lasker2014data} fit NGC 3115 with a bulge + disc + envelope, 
and measured a bulge half-light radius of $3.9~\rm arcsec$ and a bulge-to-total ratio of $0.12$. 
We describe this galaxy using a spheroid + intermediate-scale disc + nuclear ring, 
and obtain a spheroid half-light radius of $43.6~\rm arcsec$ and a spheroid-to-total ratio of $0.85$. 
We have used both kinematical information and ellipticity profiles, 
together with the surface brightness profile, 
to obtain a physically consistent and meaningful model.

@@

\subsubsection{NGC 3377}
\cite{lasker2014data} modelled the {\bf central fast rotator} NGC 3377 
{\bf (e.g.~\citealt{jedrzejewski1987inproceedings,scorzabender1995}) }
with a bulge + nuclear disc + disc + envelope, 
and obtained a bulge half-light radius of $10.1~\rm arcsec$ and a bulge-to-total flux ratio of $0.35$; 
our model with a spheroid + intermediate-scale disc + nuclear disc 
returns a spheroid half-light radius of $61.8~\rm arcsec$ and a spheroid-to-total flux ratio of $0.94$.

@@

\subsubsection{NGC 4697}
{\bf While NGC 4697 (e.g.~\citealt{carter1987,Jedrzejewski1987n720n1052n4697,davies1981}) 
was explicitly referred to as a ``fast rotator'' by \cite{capaccioli1987} and \cite{petrou1981}, 
it is only a central fast rotator} and it represents an ``extreme'' case. 
\cite{lasker2014data} fit this galaxy with a bulge + nuclear source + disc + envelope, 
and obtained a bulge half-light radius of $6.3~\rm arcsec$ and a bulge-to-total flux ratio of $0.08$; 
we described NGC 4697 using a spheroid + intermediate-scale disc + nuclear disc model, 
and measured a spheroid half-light radius of $239.3~\rm arcsec$ and a spheroid-to-total flux ratio of $0.89$. \\

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{n1332_image}
\includegraphics[width=0.49\columnwidth]{n1332_unsharp} \\
\includegraphics[width=1.03\columnwidth]{n1332_decomposition.pdf}
\caption{NGC 1332.
Similar to Figure \ref{fig:n3115}. 
The surface brightness profile extends out to seven galaxy half-light radii ($\sim 7 \times 20~\rm arcsec$). 
The empty points are data excluded from the fit. 
}
\label{fig:n1332}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.49\columnwidth]{mrk1216_image.jpeg}
\includegraphics[width=0.49\columnwidth]{mrk1216_unsharp.jpeg} \\
\includegraphics[width=1.05\columnwidth]{mrk1216_decomposition.pdf}
\caption{Mrk 1216. 
Similar to Figure \ref{fig:n3115}. 
The top panels are the \emph{HST}/WFC3 \emph{F160W} image (left) and its unsharp mask (right).
The surface brightness profile extends out to five galaxy half-light radii ($\sim 5 \times 5~\rm arcsec$). 
The color lines represent the individual (PSF-convolved) model components:
{\bf red solid = S\'ersic (spheroid), blue dashed = exponential (nuclear and intermediate-scale disc). }
}
\label{fig:m1216}
\end{center}
\end{figure}

@@

Acknowledging the correct structure of galaxies with intermediate-scale discs is important to properly understand their origin. 
According to the current paradigm of cosmological structure evolution, 
the genesis of massive early-type galaxies is characterized by two distinct phases: ``in-situ'' and ``ex-situ''. 
The first phase takes place in a young Universe (within its first $4~\rm Gyr$), 
when cold gas inflows produced short and intense bursts of star formation 
that created compact and dense conglomerates of stars with high velocity dispersion (e.g.~\citealt{prieto2013}). 
These naked and compact conglomerates, named ``red nuggets'' \citep{damjanov2009}, 
have been observed at high-redshift with half-light sizes of 1--2 kpc \citep{daddi2005,trujillo2006,vandokkum2008}.
In the second phase (last $10~\rm Gyr$), discs and stellar envelopes 
were accreted around these primordial conglomerates and the external parts of today's galaxies assembled on scales of 2--20 kpc 
(e.g.~\citealt{driver2013}). \\
Today's Universe is populated by an abundance of compact, massive spheroids, 
with the same physical properties -- mass and compactness -- as the high-redshift red nuggets \citep{graham2013review,GDS2015}. 
Some of these local compact massive spheroids are encased within a large-scale disc, 
that is to say they are the bulges of some lenticular and spiral galaxies.  
Over the last $10~\rm Gyr$ their spheroids have evolved by growing a relatively flat disc (e.g.~\citealt{pichon2011,danovich2012,stewart2013})
-- rather than a three-dimensional envelope -- 
which has increased the galaxy size but preserved the bulge compactness. 
{\bf Of course some lenticular/ES galaxies may have been built from mergers (e.g.~\citealt{querejeta2015}, and references therein). }
The other compact massive spheroids of today's Universe belong to some galaxies with intermediate-scale discs. 
Indeed, Mrk 1216, NGC 1271, NGC 1277, NGC 1332, and NGC 3115 are all local compact intermediate-scale disc galaxies 
with purely old ($>10~\rm Gyr$) stellar populations. 
These galaxies have undergone the lowest degree of disc growth. \\
In addition to the observational clues as to the actual physical components in galaxies with intermediate-scale discs, 
one can reason on other grounds as to why these compact galaxies are not comprised of an inner bulge 
plus large-scale disc plus outer envelope. 
If they were such three-component systems, then one would have two possibilities. 
The first possibility is that these galaxies were already fully assembled $10~\rm Gyr$ ago; 
this would explain their old stellar populations, 
but it would also imply that their discs and envelopes had already formed during the first $4~\rm Gyr$ of the Universe, 
in disagreement with the current cosmological picture. 
The second possibility is that only their inner bulges (with sizes of 0.1--0.2 kpc, 
according to past decompositions) originated in the first $4~\rm Gyr$ 
and they subsequently accreted a substantial disc and envelope. 
If this was correct, then we would observe high-redshift, star-like, naked bulges with stellar masses 
within a factor of a few times the currently observed red nuggets but sizes which are $10$ times smaller. 
However, a dramatically different expectation is reached 
if one considers these galaxies today as spheroid-dominated systems with an intermediate-scale disc; 
in this case, both the galaxy size and the spheroid size are compact (1--2 kpc). 
This implies that, among the local descendants of the high-redshift red nuggets, 
the compact intermediate-scale disc galaxies have undergone the lowest degree of disc growth. 
That is, the bulk of a compact intermediate-scale disc galaxy quickly assembled ``in-situ'' in a very young Universe 
and experienced very little evolution over the last $10~\rm Gyr$.
